Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks

### 2020-03-16 paper/eccv2020submission.tex
Adding paragraph about correlation

On one hand, we are dealing with image data that is meant to be perceived by human observer. This implies that full accuracy is not essential and therefore we place the importance on the perceived qualities of the results. This makes sense as in our case a human is concerned with the general development of the simulation over time. Under those consideration have chose appropriate metrics to compare the predicted simulation frames with the real ones. In this aspect, the first of the metrics that we have chose is Peak Signal to Noise Ratio (PSNR). It is related top the mean secured error (MSE) and it's given by
\begin{equation}
PSNR = 10 \cdot \log_{10}\left(\frac{255^2}{MSE}\right)
\end{equation}
PSNR is measured in decibel (dB) and it is a common metric used to evaluate lossy compression algorithms. It measures the difference between original and reconstructed image and considers the fidelity of the reconstruction. This makes the metric suitable in our case. Typical PSNR values of lossy image and video compression  algorithms are between 30 and 50 dB.

>>>>

On one hand, we are dealing with image data that is meant to be perceived by human observer. This implies that full accuracy is not essential and therefore we place the importance on the perceived qualities of the results. This makes sense as in our case a human is concerned with the general development of the simulation over time. Under those consideration have chose appropriate metrics to compare the predicted simulation frames with the real ones. In this aspect, the first of the metrics that we have chose is Peak Signal to Noise Ratio (PSNR). It is related top the mean secured error (MSE) and it's given by
\begin{equation}
PSNR = 10 \cdot \log_{10}\left(\frac{255^2}{MSE}\right)
\end{equation}
PSNR is measured in decibel (dB) and it is a common metric used to evaluate lossy compression algorithms. It measures the difference between original and reconstructed image and considers the fidelity of the reconstruction. This makes the metric suitable in our case. Typical PSNR values of lossy image and video compression  algorithms are between $30$ and $50$ dB.

When considering the perceived image quality, we also have decided to use correlation to compare the predicted and the real simulation frames. We think that if the predicted images differ only in a factor from the real ones, the models can accurately capture the relative difference between the pixels of the target image. For this reason we opted for also evaluating the results through correlation.
